Template Master's Thesis

### 2023-08-09 paper.tex
Minor corrections to intro

\textbf{Related work}\\
Previous work in this field can be broadly distinguished between methods%heuristics
 developed for the unspent transaction output (UTXO) model (e.g, Bitcoin and ZCash) and the account-based model (e.g., Ethereum, Polygon). While both models share the concept of addresses, the notion of accounts is not present in UTXO-based blockchains. The way in which transactions are processed is fundamentally different, and therefore, clustering heuristics are not applicable to both paradigms.

A number of address clustering heuristics in the UTXO setup have been proposed for Bitcoin and derivatives \citep{Androulaki2013, Meiklejohn2013, Haslhofer2016, jourdan2018, kappos2022}. All these methods will not be the focus of this work and therefore not discussed. As suggested by \cite{nakamotoBitcoin2008} in the Bitcoin whitepaper, most Bitcoin wallet implementations use a new key pair for each transaction to keep them from being linked to a common owner. \newline
In contrast to the UTXO-model, native transactions in account-based blockchains can only move funds between a single sender and receiver, and the ``change``remains in the sender account. Subsequent transactions necessarily use the same address again. The account-based model essentially relies on address reuse on the protocol level \citep{Beres2020}. Therefore, privacy guarantees should be lower and most users likely use only a small number of addresses. \newline
% Make an assumption that people only use a small set of addresses
Clustering heuristics for account-based blockchains were first introduced by \cite{FV:17}. He proposed and applied heuristics that exploit patterns related to deposit addresses, multiple participation in airdrops, and token authorization mechanisms. \newline
\cite{Beres2020} propose more universally applicable methods, as they argue that Victor’s heuristics, while powerful, assume participation in certain on-chain events. Their technique interprets transactions or token transfers as network graphs, with addresses as nodes and asset transfers as edges. They quantitavely compare graph-representation learning algorithms (a subset of machine learning) and propose further user profiling techniques based on time-of-day activity and transaction fees. Using ENS address pairs as ground truth, the authors rigorously test their methods and apply their findings to significantly reduce the privacy guarantees of Tornado Cash, a non-custodial privacy-enhancing protocol on Ethereum. \newline
\cite{wu2022tutela} extend on one of \cite{Beres2020} graph representation learning %node-embedding
 algorithms and apply it at scale. Further, they also propose a set of new clustering heuristics targeting Tornado Cash,  showing that careless user behavior can still reveal identity. They build an application built on those heuristics to measure the anonymity of an Ethereum address. All of the methods mentioned will be discussed in greater detail in Section 3. \newline
Broadening the scope of entity identification, \cite{victorlüders2019} study the largest Ethereum ERC-20 token networks from a graph perspective. Similarly, \cite{casalebrunet2021} apply network graph analysis to various non-fungible token (NFT) ecosystems. Both find that many of the networks follow either a star or a hub-and-spoke pattern. These patterns are common to interaction graphs in social networks. Further, \cite{Payette2017} propose a segmentation of the Ethereum address space into four distinct behaviour groups sharing similar attributes using k-means clustering. \newline
Rather than treating users as entities and analyzing on-chain data, \cite{yu2023} propose a novel approach for correlation analysis by exploiting network information. Although this approach has the potential to avoid the impact of privacy-enhancing technologies, it introduces a new set of limitations and problems. Thus, this approach may be of great interest for further research, particularly when privacy-enhancing techniques become more widely used.

\textbf{Our contribution}\\
In this work, we perform entity identification on an address set containing 473,927 addresses. To obtain these addresses, a separate project collected snapshots of avatar activity in Decentraland over an ten-month period from July 2022 to April 2023. Due to Decentraland's blockchain-based architecture, each avatar contains information about a user's Web3 address. 
We test the applicability of existing heuristics, and if feasible, their efficacy in detecting entities using multiple addresses is evaluated.
The main objective is to estimate the number of real-world entities that these addresses represent. The clustering of addresses is limited to this set only, without considering any %(clusters for)
 addresses outside of it, e.g., that were not registered in Decentraland during the given time frame.
Furthermore, we introduce our own heuristics for identifying address clusters and evaluate their suitability for implementation in other contexts.
%Anwenden/discuss and evaluate existing heuristics to my specific address set.
%Anpassen, erweitern

@@

Implemented as NFTs %Currently, all the subdomains or non .eth domains are not NFT, unless the domain registrar itself supports NFT such as (dcl.eth, and .kred).

Find all addresses that transferred/minted etc. an ENS Name.
Check for each address in the list if the address points to an human-readable name.
If two addresses point to the same ENS name we consider them belonging to the same entity.

@@

To get this information, we query .

@@

>>>>

\textbf{Related work}\\
Previous work in this field can be broadly distinguished between methods %heuristics
 developed for the unspent transaction output (UTXO) model (e.g, Bitcoin and ZCash) and the account-based model (e.g., Ethereum, Polygon). While both models share the concept of addresses, the notion of accounts is not present in UTXO-based blockchains. The way in which transactions are processed is fundamentally different, and therefore, clustering heuristics are not applicable to both paradigms.

A number of address clustering heuristics in the UTXO setup have been proposed for Bitcoin and derivatives \citep{Androulaki2013, Meiklejohn2013, Haslhofer2016, jourdan2018, kappos2022}. All these methods will not be the focus of this work and therefore not discussed. As suggested by \cite{nakamotoBitcoin2008} in the Bitcoin whitepaper, most Bitcoin wallet implementations use a new key pair for each transaction to keep them from being linked to a common owner. \newline
In contrast to the UTXO-model, native transactions in account-based blockchains can only move funds between a single sender and receiver, and the ``change`` remains in the sender account. Subsequent transactions necessarily use the same address again. The account-based model essentially relies on address reuse on the protocol level \citep{Beres2020}. Therefore, privacy guarantees should be lower and most users likely use only a small number of addresses. \newline
% Make an assumption that people only use a small set of addresses
Clustering heuristics for account-based blockchains were first introduced by \cite{FV:17}. He proposed and applied heuristics that exploit patterns related to deposit addresses, multiple participation in airdrops, and token authorization mechanisms. \newline
\cite{Beres2020} propose more universally applicable methods, as they argue that Victor’s heuristics, while powerful, assume participation in certain on-chain events. Their technique interprets transactions or token transfers as network graphs, with addresses as nodes and asset transfers as edges. They quantitavely compare graph-representation learning algorithms (a subset of machine learning) and propose further user profiling techniques based on time-of-day activity and transaction fees. Using ENS address pairs as ground truth, the authors rigorously test their methods and apply their findings to significantly reduce the privacy guarantees of Tornado Cash, a non-custodial privacy-enhancing protocol on Ethereum. \newline
\cite{wu2022tutela} extend on one of \cite{Beres2020} graph representation learning %node-embedding
 algorithms and apply it at scale. Further, they also propose a set of new clustering heuristics targeting Tornado Cash,  showing that careless user behavior can still reveal identity. They build an application built on those heuristics to measure the anonymity of an Ethereum address. All of the methods mentioned will be discussed in greater detail in Section 3. \newline
Broadening the scope of entity identification, \cite{victorlüders2019} study the largest Ethereum ERC-20 token networks from a graph perspective. Similarly, \cite{casalebrunet2021} apply network graph analysis to various non-fungible token (NFT) ecosystems. Both find that many of the networks follow either a star or a hub-and-spoke pattern. These patterns are common to interaction graphs in social networks. Further, \cite{Payette2017} propose a segmentation of the Ethereum address space into four distinct behaviour groups sharing similar attributes using k-means clustering. \newline
Rather than treating users as entities and analyzing on-chain data, \cite{yu2023} propose a novel approach for correlation analysis by exploiting network information. Although this approach has the potential to avoid the impact of privacy-enhancing technologies, it introduces a new set of limitations and problems. Thus, this approach may be of great interest for further research, particularly when privacy-enhancing techniques become more widely used.

\textbf{Our contribution}\\
In this work, we perform entity identification on an address set containing 473,927 addresses. To obtain these addresses, a separate project collected snapshots of avatar activity in Decentraland over an ten-month period from July 2022 to April 2023. Due to Decentraland's blockchain-based architecture, each avatar contains information about a user's Web3 address. \newline
We test the applicability of existing heuristics, and if feasible, their efficacy in detecting entities using multiple addresses is evaluated.
The main objective is to estimate the number of real-world entities that these addresses represent. The clustering of addresses is limited to this set only, without considering any %(clusters for)
 addresses outside of it, e.g., that were not registered in Decentraland during the given time frame.
Furthermore, we introduce our own heuristics for identifying address clusters and evaluate their suitability for implementation in other contexts.
%Anwenden/discuss and evaluate existing heuristics to my specific address set.
%Anpassen, erweitern

@@

%When ENS .eth registrar migrated in May 2019, the .eth registrar became an

%Currently, all the subdomains or non .eth domains are not NFT, unless the domain registrar itself supports NFT such as (dcl.eth, and .kred). If you want to turn all subdomains which you own, you have to create a registrar

Find all addresses that transferred/minted an ENS Name.

Check for each address in the list if the address points to an human-readable name.

If two addresses point to the same ENS name we consider them belonging to the same entity.

@@

\begin{enumerate}
	\item From transfer event data, get addresses that interacted with ENS or DCL Registrar as a list
	\item For each address, find the ENS name it points to using web3.py.ens module (Infura as provider) w3.ens('0xAB') - Ens List
	\item Find addresses that point to the same human-readable name (group by ENS Name and find instances where exactly 2 addresses point to the same name)
	\item Save in a CSV (ens\_pairs.csv)
\end{enumerate}

@@

From the web3.py documentation \url{https://web3py.readthedocs.io/en/stable/ens_overview.html}
%The Ethereum Name Service (ENS) is analogous to the Domain Name Service. It enables users and developers to use human-friendly names in place of error-prone hexadecimal addresses, content hashes, and more.
%The ens module is included with web3.py. It provides an interface to look up domains and addresses, add resolver records, or get and set metadata.
